---
title: "R Markdown and Leaflet"
author: "Zhe Jiang"
date: "11/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Leaflet is one of the most popular Javascript libraries for
creating interactive maps. The leaflet R package allows you
to create your own leaflet maps without needing to know any
Javascript!

In this smnall project, I will show all the location of 10 Universitiy of California with customized logo with corresponding popup logos and main webstite.

## Load necessary libraries
```{r message = FALSE}
library(leaflet)
library(dplyr)
```


Create Data Frame with campus name and exact location (lattitude and longitute)
```{r}
UCLatLong <- data.frame(
    campus = c("UCI","UCLA","UCB","UCSD","UCD",
               "UCSB","UCR","UCM","UCSC","UCSF"),
    lat = c(33.6482,34.0702,37.8719,32.8780,38.5382,
            34.4140,33.9737,37.3642,36.9741,37.7631),
    lng = c(-117.8420,-118.4453,-122.2594,-117.2347,-121.7617,
            -119.8489,-117.3281,-120.4255,-122.0308,-122.4578))
```

Create specific icon list with customize size
```{r}
w = 60
h = 30
UCIcons <- iconList(
    makeIcon(iconUrl = "./logos/UCI.png", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCLA.png", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCB.png", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCSD.png", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCD.png", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCSB.png", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCR.png", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCM.jpg", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCSC.jpg", iconWidth = w, iconHeight = h),
    makeIcon(iconUrl = "./logos/UCSF.png", iconWidth = w, iconHeight = h)
)
```

Create PopUp parameters with correspoinding website.
```{r}
UCSites <- c(
  "<a href='http://www.uci.edu/'>UC Irvine</a>",
  "<a href='http://www.ucla.edu/'>UCLA</a>",
  "<a href='http://www.berkeley.edu/'>UC Berkerly</a>",
  "<a href='http://www.ucsd.edu/'>UCSD</a>",
  "<a href='http://www.ucdavis.edu/'>UC Davis</a>",
  "<a href='http://www.ucsb.edu/'>UCSB</a>",
  "<a href='http://www.ucr.edu/'>UC Riverside</a>",
  "<a href='http://www.ucmerced.edu/'>UC Merced</a>",
  "<a href='http://www.ucsc.edu/'>UCSC</a>",
  "<a href='http://www.ucsf.edu/'>UCSF</a>"
)
```

let' see how all UC campuses are distributed in California.

```{r fig.align = 'center'}
UCLatLong %>% 
    leaflet() %>% 
    addTiles() %>%
    addMarkers(icon = UCIcons, popup = UCSites)
```
